upwell_IDX

### 2020-04-30 upwell_IDX.Rmd
deleted code

wind_daily_tested <- wind_data %>% 
  filter(temp_sites %in% selected_sites) #%>%  # Matching the sites to wind temp sites
  # dplyr::group_by(temp_sites, date) 
# save(wind_daily_tested, file = "Data_coast_angle/wind_daily_tested.RData")

# The data provided by SAWS already reads wind from the direction which it is blowing
# RWS: Great find on this timeAverage function!
wind_daily <- timeAverage(wind_daily_tested, avg.time = "day", type = "temp_sites", vector.ws = TRUE)
save(wind_daily, file = "Data_coast_angle/wind_daily.RData")
```

@@

# Determining the angle perpendicular to the coastline and plotting it

<!-- RWS: This section is no longer necessary as we decided to go with the static value of 160 -->

```{r}
# Coast R- function that calculates the angle of the site perpendicular to the coastline
# Transect function in coastR package finds the angle away or along the coastline
south_africa_along_wide <- coastR::transects(site_list_sub, spread = 30, alongshore = T) 
south_africa_away_wide <- coastR::transects(site_list_sub, spread = 30, alongshore = F) %>% 
  mutate(heading = ifelse(heading < 0, heading+360, heading))

# Plotting the map
world_map <- ggplot() + 
  borders(fill = "grey40", colour = "black")

# Plotting function
plot_sites <- function(site_list, buffer, dist){

  # Find the point 200 km from the site manually to pass to ggplot
  heading2 <- data.frame(geosphere::destPoint(p = select(site_list, lon, lat),
                                              b = site_list$heading, d = dist))
#
  # Add the new coordinates tot he site list
  site_list <- site_list %>%
    mutate(lon_dest = heading2$lon,
           lat_dest = heading2$lat)
#
  # Visualise
  world_map +
    geom_segment(data = site_list, colour = "red4",
                 aes(x = lon, y = lat, xend = lon_dest, yend = lat_dest)) +
    geom_point(data = site_list, size = 3, colour = "black", aes(x = lon, y = lat)) +
    geom_point(data = site_list, size = 3, colour = "red", aes(x = lon_dest, y = lat_dest)) +
    coord_quickmap(xlim = c(min(site_list$lon - buffer),
                             max(site_list$lon + buffer)),
                    ylim = c(min(site_list$lat - buffer),
                             max(site_list$lat + buffer))) +
    labs(x = "", y = "", colour = "Site\norder")
}
# Perpendicular transects
south_africa_away <- plot_sites(south_africa_away_wide, 1, 100000)
south_africa_away

# SHore normal transects
south_africa_along <- plot_sites(south_africa_along_wide, 1, 100000)
south_africa_along
```

@@

```{r}
# RWS: the cos() function works on radians, not degrees.
UI_angle <- wind_daily %>% # Making reference to the wind daily data created above
  dplyr::rename(site = sites) %>%  # Renaming sites to site
  #left_join(south_africa_away_wide[,c(2,21)], by = "site") %>%  # Joining wind data to South Africa wide data column 2 and 21. by site 
  drop_na() %>% # removing the na values
  #dplyr::rename(coast_angle = heading) %>% # Renaming the column heading to coast_angle
  mutate(ui.saws = mean_speed * (cos(deg_rad(dir - 160)))) %>% # This is the orientation of the coastal angle for the west coast
  dplyr::rename(t = date) %>% # renaming date to t
  drop_na()
# save(UI_angle, file = "Data_coast_angle/UI_angle.RData")
# save(UI_angle, file = "Data/UI_angle.RData")

# RWS: Can the following code be deleted now?
# index <- wind_UI %>%
#   group_by(site) %>%
#   select("date", "ui.saws") %>%
#   mutate(saws.condition = ifelse(ui.saws < 12.5, "upwelling"))
# wind_UI <- wind_daily %>% 
#   mutate(ui.saws = mean_speed * (cos(dir_circ - 160))) %>% # 160 is angle perpendicular to the west coast of SA (See paper Fielding and Davis pg 182)
#   drop_na
# Results obtained from UI_angle (Using the perpendicular angle for each site) and the results of wind_UI at -160 (angle of the west coast) appears to be the same
```

>>>>

wind_daily_tested <- wind_data %>% 
  filter(temp_sites %in% selected_sites) #%>%  # Matching the sites to wind temp sites
  # dplyr::group_by(temp_sites, date) 
# save(wind_daily_tested, file = "Data_coast_angle/wind_daily_tested.RData")
# The data provided by SAWS already reads wind from the direction which it is blowing
# RWS: Great find on this timeAverage function!
wind_daily <- timeAverage(wind_daily_tested, avg.time = "day", type = "temp_sites", vector.ws = TRUE)
save(wind_daily, file = "Data_coast_angle/wind_daily.RData")
```

@@

@@

```{r}
# RWS: the cos() function works on radians, not degrees.
UI_angle <- wind_daily %>% # Making reference to the wind daily data created above
  dplyr::rename(site = sites) %>%  # Renaming sites to site
  #left_join(south_africa_away_wide[,c(2,21)], by = "site") %>%  # Joining wind data to South Africa wide data column 2 and 21. by site 
  drop_na() %>% # removing the na values
  #dplyr::rename(coast_angle = heading) %>% # Renaming the column heading to coast_angle
  mutate(ui.saws = mean_speed * (cos(deg_rad(dir - 160)))) %>% # This is the orientation of the coastal angle for the west coast
  dplyr::rename(t = date) %>% # renaming date to t
  drop_na()
# save(UI_angle, file = "Data_coast_angle/UI_angle.RData")
# save(UI_angle, file = "Data/UI_angle.RData")
```
